Optogenetic Maxwell Demon to Exploit Intrinsic Noise and Control Cell Differentiation Despite Time Delays and Extrinsic Variability

### 2023-05-04 paper.tex
update

Dynamic reference targeting was performed by cycling though individual controllers which were optimized to a single target point at a fixed frequency. Thirty-two controllers were optimized along a pathway in order to target an in-sync reference point \ref{CR}(Synchronous), a phase lagged reference point \ref{CR}(Phase Lagged), or frequency separated reference point\ref{CR}(Phase Lagged and Frequency). 
The in phase signal is given by $r(t)=[10 sin (2\pi f t)+20, 10 sin (2\pi f t)+20]$, the phase-lagged signal is given by $r(t)=[10 sin (2\pi f t)+20, 10 cos (2\pi f t)+20]$, and the frequency driven signal is given by $r(t)=[10 sin (2\pi f t)+20, 10 sin (3\pi f t)+20]$ FSP simulations of cyclically driven systems were slowly driven at a frequency of 1/5000 seconds and their medians are shown in the Fig \ref{CR}(A4, B4,C4)(red cloud, blue cloud). Root mean squared error of each simulation are shown in Fig \ref{CR}(A5, B5,C5). Simulations show that in-phase control performed the best with an RSME of 7.0 despite moving over the unstable point in the system. When the system is driven with a phase-lag the RSME of the score increases to 8.3 and when driven at a different frequency the RMSE goes up to $9.1$.

\begin{figure*}
\begin{center}
\includegraphics[width=1\textwidth]{ControlReferenceGranularity.pdf}
\vspace{-0.1in}
\caption{Stochastic simulations driven using a phased lagged controller show improved score at high granularity and low frequency.}
\label{CRG}
\end{center}
\vspace{-0.2in}
\end{figure*}
Although the control of a dynamic reference point using a Piecewise controller is possible, the effect of cycling frequency is also important.
16 SSA simulations of the phase-separated driving controller were performed on a system over a two dimensional domain of points $(\alpha,f)$ for a time of XXX minutes. Comparisons of control performance at $\alpha=0.5$ and $\alpha=2.0$ (Fig \ref}{CRG} (C))show that control performance improves with system scale. 16 SSA simulations of the high granularity system driven by phase-lag were performed over a range of frequency values.  These analysis show that at low frequency the systems have a noise floor which decreases with increasing alpha, but was the system were driven rapidly, all systems became equally uncontrollable. At high frequency, the scores never got worse than $J=650$. At high frequency the control performance plateaus, while at lower frequency the system improves with increasing $\alpha$ Fig \ref{CRG}(E).

>>>>

Dynamic reference targeting was performed by cycling though individual controllers which were optimized to a single target point at a fixed frequency. Thirty-two controllers were optimized along a pathway in order to target an in-sync reference point \ref{CR}(Synchronous), a phase lagged reference point \ref{CR}(Phase Lagged), or frequency separated reference point\ref{CR}(Phase Lagged and Frequency). 
The in phase signal is given by $r(t)=XXX$, the phase-lagged signal is given by $r(t)=XXX$, and the frequency driven signal is given by $r(t)=XXX$ FSP simulations of cyclically driven systems were slowly driven at a frequency of 1/5000 seconds and their medians are shown in the Fig \ref{CR}(A4, B4,C4)(red cloud, blue cloud). Root mean squared error of each simulation are shown in Fig \ref{CR}(A5, B5,C5). Simulations show that in-phase control performed the best with an RSME of $7.0$ despite moving over the unstable point in the system. When the system is driven with a phase-lag the RSME of the score increases to $8.3$ and when driven at a different frequency the RMSE goes up to $9.1$.

\begin{figure*}
\begin{center}
\includegraphics[width=1\textwidth]{ControlGranularityAndFrequency.pdf}
\vspace{-0.1in}
\caption{Stochastic simulations driven using a phased lagged controller show improved score at high granularity and low frequency.}
\label{CRG}
\end{center}
\vspace{-0.2in}
\end{figure*}
Although the control of a dynamic reference point using a Piecewise controller is possible, the effect of cycling frequency is also important.

16 SSA simulations of the phase-separated driving controller were performed on a system over a two dimensional domain of points $(\alpha,f)$ for a time of XXX minutes. Comparisons of control performance at $\alpha=0.5$ and $\alpha=2.0$ (Fig (C))show that control performance improves with system scale. 16 SSA simulations of the high granularity system driven by phase-lag were performed over a range of frequency values.  These analysis show that at low frequency the systems have a noise floor which decreases with increasing alpha, but was the system were driven rapidly, all systems became equally uncontrollable. At high frequency, the scores never got worse than $J=650$. At high frequency the control performance plateaus, while at lower frequency the system improves with increasing $\alpha$ Fig(E).
